### 2015-07-05 auspice/intro.tex
added shrink, auspice, first draft background, intro edited
added abstract, small reference fixes in rest of thesis.

%!TEX root = Main.tex
\vsp
\section{Introduction}
\label{sec:intro}
``Mobile'' has long arrived, but the Internet remains unmoved. Today, there is roughly one cellphone per human; the number of smartphones sold last year alone roughly equals the number of wired hosts on the Internet \cite{gartner}; and the total traffic originated by mobiles is poised to approach that by wired devices \cite{cisco-vni}. However, the current Internet continues to operate as it did when dominated by tethered hosts, simply ignoring frequent endpoint mobility.

@@

But a key missing element from this package today is a distributed name resolution infrastructure that can scale to orders of magnitude higher update rates than envisioned when DNS was created. To appreciate the envisioned scale, consider tens of billions of mobile identifiers changing network addresses at least tens of times per day. DNS's heavy reliance on TTL-based caching, a key strength recognized by its creators, researchers, and operators alike, poses a significant handicap by increasing update propagation delays, load on name servers, and overall client-perceived latency. It is not uncommon for DNS update propagation to take a day or more, resulting in long  outage times when online services have to be moved unexpectedly, prompting cries for help on operator forums \cite{serverfault,dns-long-update}. A less widely noted limitation of DNS is its reliance on hierarchical names for scaling via federation and its single root of trust, which constrains mobile applications from selecting arbitrary application-specific names (as elaborated in $\S$\ref{sec:whyNotDNS} and $\S$\ref{sec:design_overview}).

@@

Our position is that seamless support for mobility requires a logically centralized global name service that rapidly translates identities to locations irrespective of how exactly identities and locations are individually represented. Our primary contribution is the design, implementation, and evaluation of \auspice, a distributed system that helps address this challenge. Compared to today's ICANN/DNS-based approach, our approach cleanly separates name resolution from adjudication and certification issues ($\S$\ref{sec:design_overview}). \auspice\ is also deployable as a managed DNS provider in today's Internet; compared to them, a key strength of \auspice\ is a {\em demand-aware} replica placement engine that significantly reduces the {\em time-to-connect} to mobile destinations in a cost-effective manner. Under light load, \auspice's demand-aware replica placement aggressively uses available resources to massively replicate name records, while under heavy load, it carefully controls the number and choice of replica locations based on the read-write patterns and pockets of high demand for each name.

@@

We have implemented a prototype of \auspice\ as a geo-distributed key-value store to serve as a flexible name resolution service for the current Internet as well as several ``future'' Internet or endpoint architectures such as MobilityFirst\cite{MobilityFirst}, HIP\cite{HIP}, or XIA\cite{XIA}. We have extensively evaluated \auspice\  using a combination of Planetlab, emulation clusters, and Amazon EC2.  Our contributions are as follows.
\begin{enumerate}
\item A case for a global name service as an indispensable part of any Internetwork design with intrinsic support for high mobility ($\S$\ref{sec:case}).
\vsp
\item \auspice, a scalable, geo-distributed, federated global name service that significantly reduces the time-to-connect under any given resource constraints despite high mobility and arbitrary endpoint identifiers ($\S$\ref{sec:design},$\S$\ref{sec:eval}). 
\figvsp
\item A proof-of-concept demonstration of intrinsic support for---{\em(i)} all four types of endpoint mobility; {\em(ii)} novel context-aware delivery primitives that generalize name- or address-based communication---over the current Internet as well as MobilityFirst \cite{MobilityFirst} ($\S$\ref{sec:e2e}). 
\vsp
\item Comparison against several best-of-breed managed DNS services showing that \auspice's  demand-aware approach significantly lowers time-to-connect and/or update cost even for today's (hardly mobile) domain names ($\S$\ref{sec:managed}).
\vsp
\end{enumerate}
\vsp

To provide a historical perspective, until the early 80s, the Internet relied on a system called \verb+HOSTS.TXT+ for name resolution, which was simply a centrally maintained text file distributed to all hosts. The current Internet's distributed DNS  arose in response to the rapidly increasing file size and distribution costs. Mockapetris and Dunlap \cite{DNS} point to TTL-based caching to reduce load and response times as a key strength, noting that ``{\em{the XEROX system {\em [Grapevine \cite{grapevine}]} was then ... the most sophisticated name service in existence, but it was not clear that its heavy use of replication, light use of caching ... were appropriate}}''. We have since come a full circle, turning to  active replication ($\S$\ref{sec:whyNotDNS}) in \auspice\ in order to address the challenges of mobility, a concern that wasn't particularly pressing  in the 80s. Compared to classical systems like Grapevine or ClearingHouse, \auspice\ enables support for automated {\em demand-aware} replica placement for {\em arbitrary names} (using several modern design elements such as consensus, the key-value abstraction, self-certifying names, consistent hashing, etc).  \auspice, through its support for context-aware delivery, is also a step towards addressing some of the challenges to which Lampson alludes on representing ``descriptive names" \cite{Lampson}.

@@

Our primary contribution is the design and implementation of a global name service that addresses the above problems. This global name service is a central component of MobilityFirst, a clean-slate future Internet architecture that is primarily motivated by the dual concerns of {\em mobility} and {\em security}.
%two concerns that are remarkable both for their absence in the design philosophy underlying the current Internet \cite{Clark88} as well as their immense importance today. 
MobilityFirst cleanly separates identity and location using a {\em globally unique identifier} (GUID) that, unlike an IP address, is by design devoid of location or any other structured information. Information about a GUID's location or {\em network address} (NA) is maintained by the resolution service. Both GUID and NA are {\em self-certifying}, i.e., they are one-way hashes of public keys, allowing any network entity to authenticate an entity claiming to possess a GUID or NA. Thus, the structureless nature of these identifiers enhances mobility as well as security. Section \ref{sec:MF} describes how the name service helps efficiently support a number of other functions such as multihoming, incoming traffic engineering, content retrieval, network mobility, multicast, etc.

@@

\paragraph{Roadmap} The rest of this paper is organized as follows. Section \ref{sec:MF} presents the naming subsystem in the MobilityFirst Internet architecture. Section \ref{sec:auspice} presents the design goals and architecture of an automated service replica placement system, \auspice, for geo-distributed cloud-hosted services and the instantiation of a global name service using it. Section \ref{sec:eval} describes the datasets used and the experimental evaluation of \auspice. Section \ref{sec:related} describes related work and Section \ref{sec:concl} concludes.

>>>>

%!TEX root = Main.tex

\chapter{A Global Name Service for a Highly Mobile Internetwork}
\label{ch:intro-auspice}

``Mobile'' has long arrived, but the Internet remains unmoved. Today, there is roughly one cellphone per human; the number of smartphones sold last year alone roughly equals the number of wired hosts on the Internet \cite{gartner}; and the total traffic originated by mobiles is poised to approach that by wired devices \cite{cisco-vni}. However, the current Internet continues to operate as it did when dominated by tethered hosts, simply ignoring frequent endpoint mobility.

@@

But a key missing element from this package today is a distributed name resolution infrastructure that can scale to orders of magnitude higher update rates than envisioned when DNS was created. To appreciate the envisioned scale, consider tens of billions of mobile identifiers changing network addresses at least tens of times per day. DNS's heavy reliance on TTL-based caching, a key strength recognized by its creators, researchers, and operators alike, poses a significant handicap by increasing update propagation delays, load on name servers, and overall client-perceived latency. It is not uncommon for DNS update propagation to take a day or more, resulting in long  outage times when online services have to be moved unexpectedly, prompting cries for help on operator forums \cite{serverfault,dns-long-update}. A less widely noted limitation of DNS is its reliance on hierarchical names for scaling via federation and its single root of trust, which constrains mobile applications from selecting arbitrary application-specific names (as elaborated in Section \ref{sec:whyNotDNS} and Section \ref{sec:design_overview}).

@@

Our position is that seamless support for mobility requires a logically centralized global name service that rapidly translates identities to locations irrespective of how exactly identities and locations are individually represented. Our primary contribution is the design, implementation, and evaluation of \auspice, a distributed system that helps address this challenge. Compared to today's ICANN/DNS-based approach, our approach cleanly separates name resolution from adjudication and certification issues (Section \ref{sec:design_overview}). \auspice\ is also deployable as a managed DNS provider in today's Internet; compared to them, a key strength of \auspice\ is a {\em demand-aware} replica placement engine that significantly reduces the {\em time-to-connect} to mobile destinations in a cost-effective manner. Under light load, \auspice's demand-aware replica placement aggressively uses available resources to massively replicate name records, while under heavy load, it carefully controls the number and choice of replica locations based on the read-write patterns and pockets of high demand for each name.

@@

We have implemented a prototype of \auspice\ as a geo-distributed key-value store to serve as a flexible name resolution service for the current Internet as well as several ``future'' Internet or endpoint architectures such as MobilityFirst\cite{MobilityFirst}, HIP\cite{HIP}, or XIA\cite{XIA}. We have extensively evaluated \auspice\  using a combination of Planetlab, emulation clusters, and Amazon EC2.  Our contributions are as follows.
\begin{enumerate}
\item A case for a global name service as an indispensable part of any Internetwork design with intrinsic support for high mobility (Section \ref{sec:case}).

\item \auspice, a scalable, geo-distributed, federated global name service that significantly reduces the time-to-connect under any given resource constraints despite high mobility and arbitrary endpoint identifiers (Section \ref{sec:design},Section \ref{sec:eval}).

\item A proof-of-concept demonstration of intrinsic support for---{\em(i)} all four types of endpoint mobility; {\em(ii)} novel context-aware delivery primitives that generalize name- or address-based communication---over the current Internet as well as MobilityFirst \cite{MobilityFirst} (Section \ref{sec:e2e}).

\item Comparison against several best-of-breed managed DNS services showing that \auspice's  demand-aware approach significantly lowers time-to-connect and/or update cost even for today's (hardly mobile) domain names (Section \ref{sec:managed}).

\end{enumerate}

To provide a historical perspective, until the early 80s, the Internet relied on a system called \verb+HOSTS.TXT+ for name resolution, which was simply a centrally maintained text file distributed to all hosts. The current Internet's distributed DNS  arose in response to the rapidly increasing file size and distribution costs. Mockapetris and Dunlap \cite{DNS} point to TTL-based caching to reduce load and response times as a key strength, noting that ``{\em{the XEROX system {\em [Grapevine \cite{grapevine}]} was then ... the most sophisticated name service in existence, but it was not clear that its heavy use of replication, light use of caching ... were appropriate}}''. We have since come a full circle, turning to  active replication (Section \ref{sec:whyNotDNS}) in \auspice\ in order to address the challenges of mobility, a concern that wasn't particularly pressing  in the 80s. Compared to classical systems like Grapevine or ClearingHouse, \auspice\ enables support for automated {\em demand-aware} replica placement for {\em arbitrary names} (using several modern design elements such as consensus, the key-value abstraction, self-certifying names, consistent hashing, etc).  \auspice, through its support for context-aware delivery, is also a step towards addressing some of the challenges to which Lampson alludes on representing ``descriptive names" \cite{Lampson}.

@@

Our primary contribution is the design and implementation of a global name service that addresses the above problems. This global name service is a central component of MobilityFirst, a clean-slate future Internet architecture that is primarily motivated by the dual concerns of {\em mobility} and {\em security}.
%two concerns that are remarkable both for their absence in the design philosophy underlying the current Internet \cite{Clark88} as well as their immense importance today. 
MobilityFirst cleanly separates identity and location using a {\em globally unique identifier} (GUID) that, unlike an IP address, is by design devoid of location or any other structured information. Information about a GUID's location or {\em network address} (NA) is maintained by the resolution service. Both GUID and NA are {\em self-certifying}, i.e., they are one-way hashes of public keys, allowing any network entity to authenticate an entity claiming to possess a GUID or NA. Thus, the structureless nature of these identifiers enhances mobility as well as security. Section \\ref{sec:MF} describes how the name service helps efficiently support a number of other functions such as multihoming, incoming traffic engineering, content retrieval, network mobility, multicast, etc.

@@

\paragraph{Roadmap} The rest of this paper is organized as follows. Section \\ref{sec:MF} presents the naming subsystem in the MobilityFirst Internet architecture. Section \\ref{sec:auspice} presents the design goals and architecture of an automated service replica placement system, \auspice, for geo-distributed cloud-hosted services and the instantiation of a global name service using it. Section \\ref{sec:eval} describes the datasets used and the experimental evaluation of \auspice. Section \\ref{sec:related} describes related work and Section \\ref{sec:concl} concludes.

### 2015-07-05 auspice/related.tex
added abstract, small reference fixes in rest of thesis.

Our work draws on lessons learned from an enormous body of prior work on network architecture as well as distributed systems, as described in $\S$\ref{sec:intro} and $\S$\ref{sec:bg}. We discuss related work not covered elsewhere in the paper here.

@@

Vu et al. describe DMap \cite{VuICDCS12}, an in-network DHT scheme %to map a self-certifying identifier to a fixed number of resolver locations using different consistent hash functions with clients choosing the closest mapped resolver. This approach 
that is similar in spirit to \staticthree\ as evaluated in our experiments ($\S$\ref{sec:eval}) (with a more direct comparison in \cite{techreport}), showing that demand-aware placement can dramatically outperform randomized placement. A more important qualitative distinction is that DMap ties federation to the interconnection structure between ISPs, which entails commensurate lookup latency penalties and potential incentive mismatches by mapping GUIDs to non-provider ISPs. In comparison, the \auspice\ approach decouples the federation structure between GNS providers from that between ISPs.

@@

\textbf{Dynamic placement.} We were unable to find prior systems that {\em automatically} reconfigure the {\em geo-distributed} replica locations of frequently {\em mutable objects} while preserving {\em consistency} (i.e., those satisfying all four italicized properties). However, reconfigurable placement has been studied for static or slow changing content \cite{gwertzman:95b} or within a single datacenter, or without replication. For example, Volley \cite{volley} optimizes the placement of mutable data objects based on the geo-distribution of accesses and is similar in spirit to \auspice\ in this respect, however it implicitly assumes a single replica for each object, so it does not have to worry about high update rates or replica coordination overhead. %As shown in  $\S$\ref{sec:eval}, creating multiple replicas of objects or services can significantly reduce user-perceived response times while also enhancing opportunities to balance load provided update cost is taken into account.
%\auspice\ is also similar in spirit to edge services hosted by CDNs. However, unlike \auspice, the geo-distributed locations of edge services as well as cloud-hosted services today are chosen manually and infrequently updated. %In comparison, \auspice\ automates geo-distributed placement of replicas, but the ``service'', a key-value store, is much simpler compared to black-box cloud-hosted services.

@@

%Theoretical works have studied many variants of facility location location problems that, like the formulation in Section \ref{sec:design}, are in general computationally hard. Some facility location problems lend themselves to efficient approximation algorithms \cite{facilitylocationapprox}. It is unclear if the formulations in Section \ref{sec:design} allow for efficient approximation algorithms and it is part of ongoing work to develop approximation algorithms that lend themselves to an uncoordinated implementation across the hosted services.

>>>>

Our work draws on lessons learned from an enormous body of prior work on network architecture as well as distributed systems, as described in Section \ref{ch:intro-auspice} and Section \ref{sec:bg}. We discuss related work not covered elsewhere in the paper here.

@@

Vu et al. describe DMap \cite{VuICDCS12}, an in-network DHT scheme %to map a self-certifying identifier to a fixed number of resolver locations using different consistent hash functions with clients choosing the closest mapped resolver. This approach 
that is similar in spirit to \staticthree\ as evaluated in our experiments (Section \ref{sec:eval}) (with a more direct comparison in \cite{techreport}), showing that demand-aware placement can dramatically outperform randomized placement. A more important qualitative distinction is that DMap ties federation to the interconnection structure between ISPs, which entails commensurate lookup latency penalties and potential incentive mismatches by mapping GUIDs to non-provider ISPs. In comparison, the \auspice\ approach decouples the federation structure between GNS providers from that between ISPs.

@@

\textbf{Dynamic placement.} We were unable to find prior systems that {\em automatically} reconfigure the {\em geo-distributed} replica locations of frequently {\em mutable objects} while preserving {\em consistency} (i.e., those satisfying all four italicized properties). However, reconfigurable placement has been studied for static or slow changing content \cite{gwertzman:95b} or within a single datacenter, or without replication. For example, Volley \cite{volley} optimizes the placement of mutable data objects based on the geo-distribution of accesses and is similar in spirit to \auspice\ in this respect, however it implicitly assumes a single replica for each object, so it does not have to worry about high update rates or replica coordination overhead. %As shown in  Section \ref{sec:eval}, creating multiple replicas of objects or services can significantly reduce user-perceived response times while also enhancing opportunities to balance load provided update cost is taken into account.
%\auspice\ is also similar in spirit to edge services hosted by CDNs. However, unlike \auspice, the geo-distributed locations of edge services as well as cloud-hosted services today are chosen manually and infrequently updated. %In comparison, \auspice\ automates geo-distributed placement of replicas, but the ``service'', a key-value store, is much simpler compared to black-box cloud-hosted services.

@@

%Theoretical works have studied many variants of facility location location problems that, like the formulation in Section \\ref{sec:design}, are in general computationally hard. Some facility location problems lend themselves to efficient approximation algorithms \cite{facilitylocationapprox}. It is unclear if the formulations in Section \\ref{sec:design} allow for efficient approximation algorithms and it is part of ongoing work to develop approximation algorithms that lend themselves to an uncoordinated implementation across the hosted services.

### 2015-07-05 ncdnpaper/LinearPrograms.tex
added abstract, small reference fixes in rest of thesis.

\begin{table}[t]
\begin{small}
\begin{center}
\begin{tabular}{|p{4.65in}|} 
 \hline
\textbf{Input variables and descriptions}\\ 
\end{tabular}
\begin{tabular}{|p{0.2in}|p{4.3in}|}
\hline
  $V$ & Set of nodes where each node represents a PoP   \\
  $E$ & Set of edges where each link represents a communication link   \\
   $o$ & Virtual origin node that hosts all the content in $K$  \\ 
%  $ X(o)$ & $X(o) \in V$  s.t., $o \in O$ is connected to $X(o)$ with infinite capacity link.\\ 
   % $ X$ & $X  \subset V$.   Each $x\in X$ is connected to unique $o \in O$  and vice versa.\\ 
  $ X$ & Set of exit nodes in $V$ \\ 
  $D_i$ & Disk capacity at node $i \in V$ (in bytes) \\
  $C_e$ & Capacity of link $e \in E$ (in bits/sec)\\
  $K$ & the set of all content accessed by end-users \\
   $S_k$ & Size of content $k \in K$.   \\
   $T_{ik}$ & Demand (in bits/sec)  at  node $i \in V$ for content $k \in K$ \\
  % $P(i)$ & Set of  outgoing links at PoP $i \in V$\\
   %$Q(i)$ & Set of  incoming links at PoP $i \in V$\\
   \hline
   \end{tabular}
\begin{tabular}{|p{4.65in}|}
  \hline
\textbf{Decision variables and descriptions}\\ 
\end{tabular}
\begin{tabular}{|p{0.2in}|p{4.3in}|}
\hline
$\alpha$ & MLU of the network \\
$z_k$ & Binary variable indicating whether one or more copies of content $k$ is placed in the network\\
$x_{jk}$ & Binary variable indicating whether content $k$  is placed at node $j \in V \cup \{o\}$\\
$f_{ij}$ & Total traffic from node $j$ to node $i$\\
$f_{ije}$ & Traffic from node $j$ to node $i$ crossing link $e$.\\
$t_{ijk}$ & Traffic demand at node $i \in V$ for content $k\in K$ served from node $j \in V \cup \{o\}$ \\\hline
\end{tabular}
\end{center}
\end{small}
\label{table:paramtable}
\caption{List of input  and decision variables for the \ncp\ problem formulation.}
\vspace{-0.2in}
\end{table}

@@

We present here a joint optimization strategy for NCDN-management formulated as a MIP. 
This formulation takes as input a content matrix, i.e., the demand for each content at each network point-of-presence (PoP), and  computes content placement, request redirection and routing that minimizes an NCDN cost function  while respecting link capacity and storage constraints.
The decision variables for this problem are listed in  Table 1. The MIP to minimize an NCDN cost function $C$ (either MLU or latency) is as follows:
\begin{equation}
\min  C
\end{equation}
\begin{equation*}
\mbox{subject to}
\end{equation*}
\begin{eqnarray}
\sum_{j \in V }  t_{ijk} +   t_{iok} &=& T_{ik}, \quad \forall k \in K, i \in V\\
\sum_{k \in K} t_{ijk} &=& f_{ij} ,  \ \forall j \in V-X, i \in V\\
\sum_{k \in K} t_{ijk} + \sum_{k \in K} \delta_{ij}  t_{iok} &=& f_{ij} ,  \ \forall j \in X, i \in V
\end{eqnarray}
where $\delta_{ij}$ is 1 if $j$ is the closest exit node to $i$ and 0 otherwise. Note that $\delta_{ij}$ is not a variable but a constant that is determined by the topology of the network, and hence constraint (4) is linear.
\begin{eqnarray}
 \sum_{p \in P(l)} f_{ijp} - \sum_{q \in Q(l)}  f_{ijq}  =  \begin{cases}  f_{ij} & \text{if } l=i,  \notag \\
   -f_{ij}  &   \text{if } l=j,  \notag \\
0 & \text{otherwise}, \end{cases}\\
\forall i,j,l \in V
\end{eqnarray}
where $P(l)$ and $Q(l)$ respectively denote the set of outgoing and incoming links at node $l$.
\begin{eqnarray}
 \sum_{i \in V, j \in V} f_{ije} &\leq& \alpha \times C_e, \quad \forall e \in E\\
 \sum_{k \in K}  x_{ik}S_k &\leq& D_i , \quad \forall i \in V\\
x_{ok} &=& 1, \quad \forall  k \in K \\
\sum_{i \in V}  x_{ik} &\geq& z_k, \quad \forall k \in K 
\end{eqnarray}
 \begin{eqnarray}
x_{ik} &\leq& z_k, \quad \forall k \in K, i \in V  
\end{eqnarray}
\vspace{-0.25in}
\begin{eqnarray}
t_{ijk} &\leq&  x_{jk} T_{ik},  \quad \forall k \in K,  i \in V, j \in V \cup \{o\}\\
t_{iok} &\leq& T_{ik}(1 - z_k), \quad  \forall   k \in K 
\end{eqnarray}
\vspace{-0.25in}
\begin{eqnarray*}
x_{jk}, \ z_k &\in& \{0,1\}, \quad \forall j \in V, k \in K\\
f_{ije}, \ t_{ijk}, \ t_{iok} &\geq& 0, \quad \forall  i,j \in V, e \in E, k\in K
\end{eqnarray*}

@@

Updating the content placement itself generates traffic and impacts the link utilization in the network. For ease of exposition, we have deferred a formal description of the corresponding constraints to a techreport  \cite{techreportNCDN}.  Finally, a simple extension to this MIP presented in a techreport \cite{techreportNCDN}  jointly optimizes routing given a TTM as well a CM.  We have presented a CM-only formulation here as our findings (in Section \ref{sec:eval}) show that a joint optimization of the CM and TTM is not useful for NCDNs.
%\subsubsection{ISP Transit Traffic Optimization}

>>>>

\begin{figure}[t]
\begin{small}
\begin{center}
\begin{tabular}{|p{4.65in}|} 
 \hline
\textbf{Input variables and descriptions}\\ 
\end{tabular}
\begin{tabular}{|p{0.2in}|p{4.3in}|}
\hline
  $V$ & Set of nodes where each node represents a PoP   \\
  $E$ & Set of edges where each link represents a communication link   \\
   $o$ & Virtual origin node that hosts all the content in $K$  \\ 
%  $ X(o)$ & $X(o) \in V$  s.t., $o \in O$ is connected to $X(o)$ with infinite capacity link.\\ 
   % $ X$ & $X  \subset V$.   Each $x\in X$ is connected to unique $o \in O$  and vice versa.\\ 
  $ X$ & Set of exit nodes in $V$ \\ 
  $D_i$ & Disk capacity at node $i \in V$ (in bytes) \\
  $C_e$ & Capacity of link $e \in E$ (in bits/sec)\\
  $K$ & the set of all content accessed by end-users \\
   $S_k$ & Size of content $k \in K$.   \\
   $T_{ik}$ & Demand (in bits/sec)  at  node $i \in V$ for content $k \in K$ \\
  % $P(i)$ & Set of  outgoing links at PoP $i \in V$\\
   %$Q(i)$ & Set of  incoming links at PoP $i \in V$\\
   \hline
   \end{tabular}
\begin{tabular}{|p{4.65in}|}
  \hline
\textbf{Decision variables and descriptions}\\ 
\end{tabular}
\begin{tabular}{|p{0.2in}|p{4.3in}|}
\hline
$\alpha$ & MLU of the network \\
$z_k$ & Binary variable indicating whether one or more copies of content $k$ is placed in the network\\
$x_{jk}$ & Binary variable indicating whether content $k$  is placed at node $j \in V \cup \{o\}$\\
$f_{ij}$ & Total traffic from node $j$ to node $i$\\
$f_{ije}$ & Traffic from node $j$ to node $i$ crossing link $e$.\\
$t_{ijk}$ & Traffic demand at node $i \in V$ for content $k\in K$ served from node $j \in V \cup \{o\}$ \\\hline
\end{tabular}
\end{center}
\label{table:paramtable}
\end{small}
\caption{List of input  and decision variables for the \ncp\ problem formulation.}
\vspace{-0.2in}
\end{figure}

@@

We present here a joint optimization strategy for NCDN-management formulated as a MIP. 
This formulation takes as input a content matrix, i.e., the demand for each content at each network point-of-presence (PoP), and  computes content placement, request redirection and routing that minimizes an NCDN cost function  while respecting link capacity and storage constraints.
The decision variables for this problem are listed in  Figure \ref{table:paramtable}. The MIP to minimize an NCDN cost function $C$ (either MLU or latency) is as follows:
\begin{equation}
\min  C
\end{equation}
\begin{equation*}
\mbox{subject to}
\end{equation*}
\begin{eqnarray}
\sum_{j \in V }  t_{ijk} +   t_{iok} &=& T_{ik}, \quad \forall k \in K, i \in V\\
\sum_{k \in K} t_{ijk} &=& f_{ij} ,  \ \forall j \in V-X, i \in V\\
\sum_{k \in K} t_{ijk} + \sum_{k \in K} \delta_{ij}  t_{iok} &=& f_{ij} ,  \ \forall j \in X, i \in V
\end{eqnarray}
where $\delta_{ij}$ is 1 if $j$ is the closest exit node to $i$ and 0 otherwise. Note that $\delta_{ij}$ is not a variable but a constant that is determined by the topology of the network, and hence constraint (4) is linear.
\begin{eqnarray}
 \sum_{p \in P(l)} f_{ijp} - \sum_{q \in Q(l)}  f_{ijq}  =  \begin{cases}  f_{ij} & \text{if } l=i,  \notag \\
   -f_{ij}  &   \text{if } l=j,  \notag \\
0 & \text{otherwise}, \end{cases}\\
\forall i,j,l \in V
\end{eqnarray}
where $P(l)$ and $Q(l)$ respectively denote the set of outgoing and incoming links at node $l$.
\begin{eqnarray}
 \sum_{i \in V, j \in V} f_{ije} &\leq& \alpha \times C_e, \quad \forall e \in E\\
 \sum_{k \in K}  x_{ik}S_k &\leq& D_i , \quad \forall i \in V\\
x_{ok} &=& 1, \quad \forall  k \in K \\
\sum_{i \in V}  x_{ik} &\geq& z_k, \quad \forall k \in K 
\end{eqnarray}
 \begin{eqnarray}
x_{ik} &\leq& z_k, \quad \forall k \in K, i \in V  
\end{eqnarray}
\vspace{-0.25in}
\begin{eqnarray}
t_{ijk} &\leq&  x_{jk} T_{ik},  \quad \forall k \in K,  i \in V, j \in V \cup \{o\}\\
t_{iok} &\leq& T_{ik}(1 - z_k), \quad  \forall   k \in K 
\end{eqnarray}
\vspace{-0.25in}
\begin{eqnarray*}
x_{jk}, \ z_k &\in& \{0,1\}, \quad \forall j \in V, k \in K\\
f_{ije}, \ t_{ijk}, \ t_{iok} &\geq& 0, \quad \forall  i,j \in V, e \in E, k\in K
\end{eqnarray*}

@@

Updating the content placement itself generates traffic and impacts the link utilization in the network. For ease of exposition, we have deferred a formal description of the corresponding constraints to a techreport  \cite{techreportNCDN}.  Finally, a simple extension to this MIP presented in a techreport \cite{techreportNCDN}  jointly optimizes routing given a TTM as well a CM.  We have presented a CM-only formulation here as our findings (in Section \ref{sec:ncdn-eval}) show that a joint optimization of the CM and TTM is not useful for NCDNs.
%\subsubsection{ISP Transit Traffic Optimization}
